Equilibria and Convergence of Fictitious Play\\ on Network Aggregative Games

### 2021-08-09 Documents/FP in NAGs/Reviews.tex
Updated Responses

	We thank the reviewer for their detailed analysis of our work. We particularly appreciate the point regarding the significance of the NA game. We will be sure to include examples and applications in our revision. To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash). This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.

@@

	We thank the reviewer for their review and their insightful comments. Regarding the contributions, our work begins by showing that  Fictitious Play converges to an equilibrium in zero-sum NA games regardless of whether or not the network has self-loops. Convergence to a Nash Equilibrium thus becomes a special case for when there are no self-loops. To show convergence, we explicitly show how the NA game can be transformed into an equivalent network game, and how the analysis extends regardless of the existence of such self-loops. Each agent can, therefore, account for their own state as well as that of their neighbours when playing the game.

	In addition, we aimed for our analysis to extend beyond the zero-sum case. It was with this in mind that we analyse the regret properties of Fictitious Play in arbitrary NA games. Specifically, Theorem 2 shows that, regardless of the number of players in the game, or the nature of the game itself, Fictitious Play will still achieve no regret. This generalises the result of van Strien and Ostrovski, which only looked at games of two players.

@@

	To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash). This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.

@@

@@

	It is indeed true that the NA game can be shown to be equivalent to the network game, and the proof of Theorem 1 is in showing the nature of this transformation. However, in making this transformation, an additional result can be found - namely that networks even with self loops can be considered and that, in this case, the techniques of Ewerhart and Valkanova can be applied to show convergence to a fixed point. This component was not realised in Ewerhart and Valkanova's work. In addition, existing results on the no regret property of Continuous Time Fictitious Play exist only in the two-player case or in specific classes of games (e.g. zero sum). The most recent contribution in this direction was that of van Strien and Ostrovski (2014) who showed the no-regret property holds in all two-player games. Our contribution generalises this result towards all NA games, regardless of the number of players or the type of game being played. The reviewer also makes an interesting suggestion to look at the discrete variant of Fictitious Play. This is indeed an interesting avenue for future research and one which we are currently exploring.

>>>>

	We thank the reviewer for their detailed analysis of our work. We particularly appreciate the point regarding the significance of the NA game. We will be sure to include examples and applications from the literature (e.g. Parise et al. 2015) in our revision. In response to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). This turns out to be true even if the NA game possesses self-loops. In such a case, it is shown that Fictitious Play still converges to a fixed point, though not always Nash. This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play in all multi-player NA games, even if Assumption 4 is not satisfied.

@@

	We thank the reviewer for their review and their insightful comments. Regarding the contributions, our work begins by showing that Fictitious Play converges to a fixed point in zero-sum NA games regardless of whether or not the network has self-loops. Convergence to a Nash Equilibrium thus becomes a special case for when there are no self-loops. Each agent can, therefore, account for their own history as well as that of their neighbours when playing the game. In a sense, the agent is able to consider itself as an opponent also. To show convergence, we explicitly show how the NA game can be transformed into an equivalent network game, and how the analysis extends regardless of the existence of such self-loops.

	In addition, we aimed for our analysis to extend beyond the zero-sum case. It was with this in mind that we analyse the regret properties of Fictitious Play in arbitrary NA games. Specifically, Theorem 2 shows that, regardless of the number of players in the game, or the nature of the game itself, Fictitious Play will still achieve no regret. This generalises the result of van Strien and Ostrovski, which only looked at games of two players. Similarly, Ewerhart and Valkanova were able to show a no-regret property for Fictitious Play which only applies in the zero-sum case, whereas Theorem 2 applies to any game.

	Finally, we conclude with some experiments which highlight an additional property of Fictitious Play. One of the more surprising results is that the presence of noise seems to lead to fixed behaviour, even in cases where the original system did not converge. The implication is that Fictitious Play in NA games may be a robust process by which multiple agents can coordinate, a topic which we suggest for future theoretical exploration.

@@

	To respond to your query, any NA game (whether or not there are self-loops) can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). Once this transformation has been applied, it is possible to show that Fictitious Play will converge to an equilibrium. Convergence to Nash thus becomes a special case for when there are no self-loops. This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated. For the case of zero-sum network games, Ewerhart and Valkanova were able to show that the no regret property holds. Theorem 2 aims to extend this analysis towards all multi-player NA games, regardless of whether Assumption 4 is satisfied.

@@

	Finally, we are grateful that the reviewer listed some of the formatting issues within the paper. We will ensure that each of these are resolved in the final submission.

@@

	It is indeed true that the NA game can be shown to be equivalent to the network game, and the proof of Theorem 1 is in showing the nature of this transformation. However, in making this transformation, an additional result can be found - namely that networks even with self loops share this equivalency and that, in this case, the techniques of Ewerhart and Valkanova can be adapted to show convergence to a fixed point. Convergence to Nash thus becomes a special case for when there are no self-loops. This point was not considered in Ewerhart and Valkanova's analysis. In addition, existing results on the no regret property of Continuous Time Fictitious Play exist only in the two-player case or in specific classes of games (e.g. zero sum). The most recent contribution in this direction was that of van Strien and Ostrovski (2014) who showed the no-regret property holds in all two-player games. Similarly, Ewerhart and Valkanova were able to prove a no-regret property in the specific case that the game is zero-sum. Our contribution in Theorem 2 generalises these results towards all NA games, regardless of the number of players or the type of game being played.

	Finally, we conclude with some experiments which highlight an additional property of Fictitious Play. One of the more surprising results is that the presence of noise seems to lead to fixed behaviour, even in cases where the original system did not converge. The implication is that Fictitious Play in NA games may be a robust process by which multiple agents can coordinate, a topic which we suggest for future theoretical exploration.

	The reviewer also makes an interesting suggestion to look at the discrete variant of Fictitious Play. This is indeed an interesting avenue for future research and one which we are currently exploring.

### 2021-08-09 Documents/FP in NAGs/neurips_2021.tex
Updated Responses

We define the \emph{state} of agent $\mu$ to be the probability
vector $\xmu \in \mathbb{R}^n$, where $\xmu_i$ is the probability
with which agent $\mu$ plays action $i$.
%It should be noted that
This
probability vector is often referred to as $\mu$'s \emph{mixed
	strategy}. With this in mind, we can construct, as their state
space, the {\em unit simplex} $\Delta_\mu$ on agent $\mu$'s action set, which
is defined
as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \mid \sum_i
\xmuaction{i} = 1\}$.

@@

  \begin{assumption}\label{ass::zerosum}
    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
    \weightedsum) = 0$ for any set $(x^\mu)_{\mu \in N^\mu}$ of
    states. This is, perhaps, one of the strongest assumptions in our
    analysis, which is required for the fixed-point analysis. However,
    in Sec.~\ref{sec::CCEConvergence}, we perform a regret analysis
    that considers the long-term behaviour of NA-CTFP without this
    assumption.
  \end{assumption}

@@

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other agent states $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

>>>>

We define the \emph{state} of agent $\mu$ to be the probability
vector $\xmu \in \mathbb{R}^n$, where $\xmu_i$ is the probability
with which agent $\mu$ plays action $i$.
%It should be noted that
This
probability vector is often referred to as $\mu$'s \emph{mixed
	strategy}. With this in mind, we can construct, as their state
space, the {\em unit simplex} $\Delta_\mu$ on agent $\mu$'s action set, which
is defined
as $\Delta_\mu := \{\xmu \in \mathbb{R}^n_+ \mid \sum_i
\xmuaction{i} = 1\}$.

@@

  \begin{assumption}\label{ass::zerosum}
    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
    \weightedsum) = 0$ for any set $(x^\mu)_{\mu \in \agentset}$ of
    states. This is, perhaps, one of the strongest assumptions in our
    analysis, which is required for the fixed-point analysis. However,
    in Sec.~\ref{sec::CCEConvergence}, we perform a regret analysis
    that considers the long-term behaviour of NA-CTFP without this
    assumption.
  \end{assumption}

@@

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other agent states $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w^{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot (w^{\mu \nu}A^\mu) x^\nu$.
